Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda \\~

### 2013-03-11 Web3D2013-Dec3D/paper.tex
added online id
Extended XML3D section.

\TOGonlineid{XXX} %TODO

@@

DFKI's XML3D \cite{Sons2010} is a similar approach. In contrast to X3DOM, this format proposes a new tag set that is not based on X3D anymore. Furthermore, it does not define a scene-graph but a strict tree structure by means of a prototyping mechanism. In recent versions of XML3D, mesh data can also be externalized from the HTML document by storing it in separate JSON files. Moreover, the developers are working on a system for dynamic data-flow to efficiently support animations \cite{KleinSJRSB12}.

>>>>

\TOGonlineid{paper1037} %TODO

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{images/museum_with_tags2.pdf}
  \caption{A highly dynamic declarative 3D scene with nine animated and skinned characters. The calculation is either performed with classical sequential JavaScript or in parallel exploiting Intel's River Trail proposal for parallel data computations in JavaScript.}
  \label{fig:xflow}
  \vspace{-0.2cm}
\end{figure}

XML3D \cite{Sons2010} is a collaboration of DFKI and Intel VCI. Similar to X3DOM, it employs CSS3, DOM scripting, DOM events, and WebGL. In contrast to X3DOM, XML3D is designed as a extension to HTML5 from scratch. It does not define a scene-graph but uses the DOM tree structure for parent child relations and second level references e.g\ via CSS to (re-)use resources such as geometry data, material descriptions or animation data. These resources are not necessarily in the same document, but can also come from external documents in various formats, e.g. as JSON files.

This generic and consistent handling of resources allows fine-granular composition of data sources. It can be combined with Xflow, a declarative data flow component~\cite{KleinSJRSB12} that allows for dynamic meshes, morphing, animation of shader parameters, image processing and AR. The data flow computation can be mapped to hardware, e.g. by composition of WebGL shaders or by exploiting available APIs such as Web Workers~\cite{w3c:webworkers} or River Trail~\cite{Herhut:2012}. Figure~\ref{fig:xflow} shows a XML3D scene with nine characters, skinned and animated with Xflow.
